The Lost Vaults: Uneasy Alliance\\\small{An online multi-user Dungeon Client and Server.}\\\small{Project Proposal for group 4}

### 2014-05-23 doc/src/proposal.tex
Preparing for final report, updated build.xml to reflect new doc directory structure, added draft.tex latex file for report draft.

\tableofcontents
\listoffigures
\newpage
\section{Introduction}
Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and because of this the way we write programs has to change. 
This new kind of architecture brings with it a new type of problems, and without adapting we will not be able to make use of the increase in processing power. 
As a way for us to explore these challenges and their solutions, we opted to work on a server-client system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive 
environment for multiple, simultaneous connections as well as multiple active and independent sections of program logic. We represent this problem through a multi-user dungeon or 
MUD, a form of online multiplayer game, where we aim to make sure that the server maintains stable performance regardless of the number of connected users.

@@

As described in the game design portion of this document, there are two types of quests: group quests and player quests. Group quests are to everyone's benefit, and player 
quests are individual quests of subterfuge. We aim to create an atmosphere where the players need to rely on each other to achieve the tougher group quests while at the same 
time remaining weary about each other as any one of them could be a traitor, looking out only for themselves and thus creating an air of an uneasy alliance as you enter the dungeon.

@@

The dungeon's room are created procedurally on demand. That is to say, a new room is only created when a player tries to enter a room that does not yet exist. There are exceptions to 
this, as will be described in the quest section of this document.
\subsubsection{Rooms}
The dungeon is made up of interconnected rooms, which may have one or more exits, each representing a door on one of the room's four walls. A room may contain any number of players, monsters 
and items. A room may also contain a ``trap'' which can be harmful as well as beneficial, performing an action on the first player to enter that room. Players may attack any other player or 
NPC occupying the same room. Combat is described in more detail below. When the combat is between players, neither player currently fighting may escape the room until one of them has fallen. 
Escaping from a battle with an NPC will cost the escaping player one extra food.
\subsubsection{Food}
Food is the main type of resource to be managed in the game as food is needed to explore the dungeon. Each player has their own supply of food, starting at a minimum of five pieces of food 
and additional food can be bought from the city merchant or be found in the dungeon. When a player enters a room that player has not yet explored, one piece of food is subtracted from their 
personal supply. Entering a room previously explored by that player does not consume food. The players' progress is therefore limited by how much food they bring with them into the dungeon.
\subsubsection{Leaving The Dungeon}
Upon leaving the dungeon, all the consumables found or brought down will be lost to the player (food and potions rot), and all treasure items that are found are sold off for gold. 
Furthermore, every player leaving a dungeon is awarded gold for the quests they have completed both as a group or individually. Dead players do not gain gold for completed quests.

@@

knows that someone has been tasked to kill someone else through the \textbf{Every ally must leave} quest. The player does not have to be the one killing the target, as long as the target 

>>>>

\tableofcontents
\listoffigures
\newpage
\section{Introduction}
Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and because of this the way we write programs has to change. 
This new kind of architecture brings with it a new type of problems and without adapting we will not be able to make use of the increase in processing power. 
As a way for us to explore these challenges and their solutions, we opted to work on a server-client system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive 
environment for multiple, simultaneous connections as well as multiple active and independent sections of program logic. We represent this problem through a multi-user dungeon or 
MUD, a form of online multiplayer game, where we aim to make sure that the server maintains stable performance regardless of the number of connected users.

@@

As described in the game design portion of this document, there are two types of quests: group quests and player quests. Group quests are to everyone's benefit and player 
quests are individual quests of subterfuge. We aim to create an atmosphere where the players need to rely on each other to achieve the tougher group quests while at the same 
time remaining weary about each other as any one of them could be a traitor, looking out only for themselves and thus creating an air of an uneasy alliance as you enter the dungeon.

@@

The dungeon's room are created procedurally at the creation of the dungeon. Each cell in a two-dimensional grid is assigned a room, and random routes connecting them to a starting room are placed 
down to ensure each room is potentially reachable, provided players have enough food.
\subsubsection{Rooms}
The dungeon is made up of interconnected rooms, which may have one or more exits, each representing a door on one of the room's four walls. A room may contain any number of players, monsters 
and items. A room may also contain a ``trap'' which can be harmful as well as beneficial, performing an action on the first player to enter that room. Players may attack any other player or 
NPC occupying the same room. Combat is described in more detail below. When the combat is between players, neither player currently fighting may escape the room until one of them has fallen. 
Escaping from a battle with an NPC will cost the escaping player one extra food.
\subsubsection{Food}
Food is the main type of resource to be managed in the game as food is needed to explore the dungeon. Each player has their own supply of food, starting at a minimum of five pieces of food 
and additional food can be bought from the city merchant or be found in the dungeon. When a player enters a room that player has not yet explored, one piece of food is subtracted from their 
personal supply. Entering a room previously explored by that player does not consume food. The players' progress is therefore limited by how much food they bring with them into the dungeon.
\subsubsection{Leaving The Dungeon}
Upon leaving the dungeon, all the consumables found or brought down will be lost to the player (food and potions rot), and all treasure items that are found are sold off for gold. 
Furthermore, every player leaving a dungeon is awarded gold for the quests they have completed both as a group or individually. Dead players do not gain gold for completed quests.

@@

knows that someone has been tasked to kill someone else through the \textbf{Every ally must survive} quest. The player does not have to be the one killing the target, as long as the target 
